A systematic comparison of interaction models for systems of cities

### 2018-09-19 Docs/CCS18/Communication/ccs2018.tex
slides
copyres

@@

Comparison of three approaches based on the evolutionary urban theory \cite{pumain1997pour} capturing different dimensions of urban systems:
\begin{itemize}
	\item The Favaro-Pumain model for the diffusion of innovation \cite{favaro2011gibrat}
	\item 
\end{itemize}

@@

>>>>

% meso / micro

% macro

\sframe{An evolutionary urban theory}{
\centering

\footnotesize
\textit{\cite{raimbault2017applied} Citation network analysis of core publications in the evolutionary urban theory}

\sframe{Towards a systematic model comparison}{

% research question

% before coupling models, benchmarking them !

\textbf{Research objective : }

@@

Comparison of three approaches based on the evolutionary urban theory \cite{pumain1997pour} capturing different dimensions of urban systems:
\begin{itemize}
	\item The Favaro-Pumain model for the diffusion of innovation \cite{favaro2011gibrat}
	\item The Marius model family based on economic exchanges \cite{cottineau2014evolution}
	\item An interaction model including physical transportation networks \cite{raimbault2018indirect}
\end{itemize}

\sframe{Datasets}{

% geodivercity harmonization of datasets

\sframe{Data preprocessing}{
\centering

Remove small cities (\cite{adam2006medium} for definition of medium-sized)

\sframe{Stylized facts}{
\centering

% - fit distributions of growth rates
% - cluster by type of distrib ?

@@

% future perspective : towards integrative theories / coupling of these models for multi-dimensional grasp of urban systems (more work needed to understand model coupling and role of parameters in fit improvement)
% Compare these models on synthetic city systems / with suited indicators (here relatively data-driven approach)
